\section{Clock distribution mezzanine}

\subsection{Overview}\label{overview}

Clock mezzanines generate high-quality RF/microwave signals for use as
data converter clocks and local oscillators (LOs) by phase-locking
low-noise VCOs to a supplied reference source. They mount on a suitable
carrier, such as \url{Baikal}, which supplies global signals to all RTMs
in a uTCA.4 rack, or to an individual RTM, such as \url{Sayma}, for
local frequency generation.

\subsection{Features and specification}\label{features-and-specification}

\begin{itemize}
	\item
	Reference input from carrier PCB via 2xSMPs, typically 100MHz
	AC-coupled differential 3V3 PECL square-wave.
	\item
	Two independent phase-locked loops (PLLs), one typically used as one
	data converter clock (CLK) and one as a high-frequency reference/local
	oscillator (REF\_LO). Outputs are AC coupled 3V3 PECL square-waves
	provided as differential signals over 2xSMPs.
	\item
	PLL lock indicators accessible via TTLs
	\item
	PLL multiplication factors (output frequencies) accessible from
	carrier via I2C
	\item
	Auxiliary CLK input from MMCX connector on top of PCB with isolated
	ground. Typical input is 50Ohm single-ended, +10dBm. Switching between
	on-board PLL and auxiliary input using integrated ultra-low noise
	clock mux controllable from carrier.
	\item
	Digital/power: copy from AFE specification, and specify pins for PLL
	locked indicators (high-locked) and mux
\end{itemize}

\subsection{Mezzanines}\label{mezzanines}

\subsubsection{Template mezzanine}\label{template-mezzanine}

Used for thermal and electrical testing of carriers, such as Sayma and
Baikal, and as a template for designing clock mezzanines.

The design files are located in
\href{https://github.com/m-labs/sinara/tree/master/ARTIQ_ALTIUM/PCB_mezzanine_clock_template}{ARTIQ\_ALTIUM/PCB\_mezzanine\_clock\_template},
the schematic is
\href{https://github.com/m-labs/sinara/blob/master/ARTIQ_ALTIUM/PCB_mezzanine_clock_template/mezzanine_clock_template.PDF}{here}.

\subsection{Low phase noise clock mezzanine}\label{low-phase-noise-clock-mezzanine}

An ultra-low noise, dual-output fixed-frequency signal generator.

The design files are located in
\href{https://github.com/m-labs/sinara/tree/master/ARTIQ_ALTIUM/PCB_mezzanine_clock}{ARTIQ\_ALTIUM/PCB\_mezzanine\_clock},
the schematic is
\href{https://github.com/m-labs/sinara/blob/master/ARTIQ_ALTIUM/PCB_mezzanine_clock_template/mezzanine_clock_template.PDF}{here}.

Specification:

\begin{itemize}

	\item
	PLL: HMC440
	\item
	VCOs: Crystek CVCO55CC family of narrow-band VCOs
	\item
	Output range for 100MHz input: 400MHz to 3.2GHz, limited by available
	VCOs and HMC440 multiplication factor
	\item
	PLL multiplication factors (output frequencies) fixed by component
	section, but readable from carrier via I2C

\end{itemize}

%\subsubsection{Loop filters}\label{loop-filters}
%
%To do: add component choices and noise models (+ measurements where
%available) for important output frequencies.

