\section{Glossary}

\begin{description}
	\item[AFE] Analogue front-end.
	\item[AMC Module or Modul] An AMC Module is a mezzanine or modular add-on card that extends the
	functionality of a Carrier Board. The term is also used to generically refer to the
	different varieties of Multi-Width and Multi-Height Modules.
	\item[BaseMod] Base-band input/output mezzanine.
	\item[COTS] Commercial off-the-shelf. Product which is designed and can be easily purchased.
	\item[EEM] Eurocard Extension Module is a Sinara standard for low-cost, low-bandwidth peripherals that are controlled by ARTIQ DRTIO.
	\item[Fat Pipes] Ports 4 though 11 of the AMC Connector constitute the Fat Pipes Region. This
	Region of Ports is intended for the assignment of multiple Lane interfaces, also
	called “fat pipes”. Fat Pipe 1 [Ports 4-7], Fat Pipe [Ports 8-11].
	\item[FMC] FPGA Mezzanine Card
	\item[HEPP] High Energy Physics. ???
	\item[Hot Swap] To remove a component (e.g., an AMC Module) from a system (e.g., an AMC Carrier
	AdvancedTCA Board) and plug in a new one while the power is still on and the
	system is still operating.
	\item[IPMB] ntelligent Platform Management Bus. The lowest level hardware management bus
	as described in the Intelligent Platform Management Bus Communications Protocol
	Specification.
	\item[Management Power or MP] The 3.3V power for a Module's Management function, individually provided to each Slot by the Carrier
	\item[MGT] Multi-Gigabit Transceiver.	
	\item[MixMod] An up-converting mezzanine, using an analogue IQ mixer to mix the input and output RF signals with a LO supplied by Sayma.
	\item[MMC] Module Management Controller. The MMC is the required intelligent controller that
	manages the Module and is interfaced to the Carrier via IPMB-Local.
	\item[RFBP] RF Backplane.
	\item[RTM] Rear Transition Module.
	\item[Sayma] Smart Arbitrary Waveform Generator, providing 8 channels of 1.2 GSPS 16-bit DACs (2.4 GHz DAC clock) and 125 MSPS 16-bit ADCs. It consists of an AMC, providing the high-speed digital logic, and a RTM, holding the data converters and analog components.
	\item[Sianra] Open-source hardware ecosystem originally designed for use in quantum physics experiments running the ARTIQ control software. It is licensed under CERN OHL v1.2.
	\item[uTCA] Micro Telecommunications Computing Architecture. MicroTCA is a modular, open standard for building high performance computer systems in a small form factor.
\end{description}


